Practical Open-Loop Optimistic Planning

### 2019-06-24 paper/main.tex
Updates from Overleaf

\let\accentvec\vec            %add before \documentclass
\documentclass[runningheads]{llncs}
\let\spvec\vec                %add before \usepackage{amsmath}
\let\vec\accentvec

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

%
\title{Practical Open-Loop Optimistic Planning}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Edouard Leurent\inst{1,2}\and
Odalric-Ambrym Maillard\inst{1}}
%
\authorrunning{E. Leurent, O-A. Maillard}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{SequeL team, INRIA Lille - Nord Europe, France\\
\email{\{edouard.leurent,odalric.maillard\}@inria.fr}\and
Renault Group, France\\
\email{edouard.leurent@renault.com}}
%
\maketitle              % typeset the header of the contribution
%

@@

\emph{Monte-Carlo Tree Search} (\texttt{MCTS}) algorithms were historically motivated by the application of computer Go, and made a first appearance in the CrazyStone software \citet{Coulom2006}. They were later reformulated in the setting of Multi-Armed Bandits by \citet{Kocsis2006} with their \emph{Upper Confidence bounds applied to Trees} (\texttt{UCT}) algorithm. Despite its popularity, \texttt{UCT} has been shown to suffer from several limitations: its sample complexity can be at least doubly-exponential for some problems (e.g. when a narrow optimal path is hidden in a suboptimal branch), which is much worse than uniform planning \citep{Coquelin2007}. The \texttt{Sparse Sampling} algorithm of \citet{Kearns2002} achieves better worst-case performance, but it is still non-polynomial and doesn't adapt to the structure of the MDP. In stark contrast, the \emph{Optimistic Planning for Deterministic systems} (\texttt{OPD}) algorithm considered by \citet{Hren2008} in the case of deterministic transitions and rewards exploits the structure of the cumulative discounted reward to achieve a problem-dependent polynomial bound on sample complexity. A similar line of work in a deterministic setting is that of \texttt{SOOP} and \texttt{OPC} by \cite{Busoniu2013,Busoniu2018} though they focus on continuous action spaces. \texttt{OPD} was later extended to stochastic systems with the \emph{Open-Loop Optimistic Planning} (\OLOP) algorithm introduced by \citet{Bubeck2010} in the open-loop setting: we only consider sequences of actions independently of the states that they lead to. This restriction in the space of policies causes a loss of optimality, but greatly simplifies the planning problem in the cases where the state space is large or infinite. More recent work such as \texttt{St0p} \citep{Szorenyi2014} and \texttt{TrailBlazer} \citep{Grill2016} focus on the probably approximately correct (PAC) framework: rather than simply recommending an action to maximise the expected rewards, they return an $\epsilon$-approximation of the value at the root that holds with high probability. This highly demanding framework puts a severe strain on these algorithms that were developed for theoretical analysis only and cannot be applied to real problems.

@@

The corresponding complexity gain compared to the original Algorithm \ref{algo:kl-olop} is: 
\begin{equation*}
    \frac{C(\texttt{Lazy KL-OLOP})}{C(\KLOLOP)} = \frac{n}{K^{L-1}}
\end{equation*}
which highlights that only a subtree corresponding to the sample budget $n$ is processed instead of the search whole tree $\Tau$.
\end{property}
\begin{proof}
At episode $m = 1, \cdots, M$, we compute and store in memory of the reward upper-bounds and U-values of all nodes in the subtree $\Tau_m^+$. Moreover, the tree $\Tau_m^+$ is constructed iteratively by adding K nodes at most L times at each episode from 0 to $m$. Hence, $|\Tau_m^+| = O(mKL)$.
This yields directly $C(\texttt{Lazy KL-OLOP}) = \sum_{m=1}^M O(mKL) = O(M^2KL)$.
\qed
\end{proof}

@@

By convention, $\mathcal{I}_0 = \{\emptyset\}$. From the definition of $\kappa_2$, we have that for any $\kappa'>\kappa_2$, there exists a constant C such that for any $h \geq 1$,
\begin{equation*}
    |\mathcal{I}_h| \leq C {\kappa'}^h
\end{equation*}
Hence, we also have $|\mathcal{J}_h| \leq K|\mathcal{I}_{h-1}| = O({\kappa'}^h)$.

@@

In order to bound this quantity, \diff{we reduce the question to the application of a deviation inequality}. For all $1\leq t\leq L$, we have on the event $\{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\}$ that $\hat{\mu}_{a^*_{1:t}}(m) \leq U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t}) < 1$. Therefore, for all $0 < \delta < 1 - \mu(a^*_{1:t})$, by definition of $U^{\mu}_{a^*_{1:t}}(m)$:

\begin{equation*}
    d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)+\delta) > \frac{f(m)}{T_{a^*_{1:t}}(m)}
\end{equation*}

As $d$ is continuous on $(0,1)\times[0, 1]$, we have by letting $\delta \leftarrow 0$ that:

\begin{equation*}
    d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)}
\end{equation*}

Since d is non-decreasing on $[\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})]$,

\begin{equation*}
    d(\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})) \geq d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)}
\end{equation*}

We have thus shown the following inclusion:

\begin{equation*}
    \{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\} \subseteq \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}}(m) \text{ and } d(\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)} \right\}
\end{equation*}

Decomposing according to the values of $T_{a^*_{1:t}}(m)$ yields:

\begin{equation*}
    \{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\} \subseteq \bigcup_{n=1}^m \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}, n} \text{ and } d(\hat{\mu}_{a^*_{1:t}, n}, \mu(a^*_{1:t})) \geq \frac{f(m)}{n} \right\}
\end{equation*}

\diff{We now apply the deviation inequality} provided in Lemma 2 of Appendix A in \citep{Cappe2013}: $\forall \epsilon > 1$, provided that $0 < \mu(a^*_{1:t}) < 1$,

\begin{equation*}
\probability{\bigcup_{n=1}^m \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}, n} \text{ and } n \dber(\hat{\mu}_{a^*_{1:t}, n}, \mu(a^*_{1:t})) \geq \epsilon \right\}} \leq e\ceil{\epsilon \log m}e^{-\epsilon}\,.
\end{equation*}

By choosing $\epsilon = f(m)$, it comes
\begin{align*}
    \probability{\eqref{eq:cond-ukl}} &\leq \sum_{t=1}^L \diff{e\ceil{f(m)\log m}e^{-f(m)}} = \diff{O(L\delta_m)}
\end{align*}

@@

\begin{lemma}[Confidence interval length and number of plays]
\label{lemma:ci-length}
Let $1 \leq h \leq L$, $a\in \mathcal{J}_h$ and $0 \leq h' < h$. Then  \eqref{eq:cond-dkl} is not satisfied if the following propositions are true:
\begin{equation}
\label{eq:sampled-enough-h}
   \forall 0\leq t\leq h', T_{a_{1:t}}(m) \geq \diff{2f(m)}(h+1)^2\gamma^{2(t-h-1)}
\end{equation}
and
\begin{equation}
\label{eq:sampled-enough}
   T_{a}(m) \geq \diff{2f(m)}(h+1)^2\gamma^{2(h'-h-1)}
\end{equation}
\end{lemma}
\begin{proof}
We start by providing an explicit upper-bound for the length of the confidence interval $U^{\mu}_{a_{1:t}} - L^{\mu}_{a_{1:t}}$. By Pinsker's inequality:

@@

Hence for all $C>0$, 
\begin{equation*}
    \dber(p, q) \leq C   \implies 2(q - p)^2 < C  \implies p - \sqrt{C/2} < q < p + \sqrt{C/2}
\end{equation*}
And thus, for all $b\in A^*$, by definition of $U^{\mu}$ and $L^{\mu}$:
\begin{align*}
    U^{\mu}_{b}(m) - L^{\mu}_{b}(m) &\leq \frac{S_b(m)}{T_b(m)} + \sqrt{\frac{f(m)}{2T_b(m)}} -  \left(\frac{S_b(m)}{T_b(m)} - \sqrt{\frac{f(m)}{2T_b(m)}}\right) 
    = \diff{\sqrt{\frac{2f(m)}{T_b(m)}}}
\end{align*}

@@

They are evaluated on the following tasks, using a discount factor of $\gamma=0.8$:
\begin{itemize}
    \item A \href{https://github.com/eleurent/highway-env/}{highway driving} environment \citep{Leurent2018}: a vehicle is driving on a road randomly populated with other slower drivers, and must make their way as fast as possible while avoiding collisions by choosing on the the following actions: \texttt{change-lane-left}, \texttt{change-lane-right}, \texttt{no-op}, \texttt{faster}, \texttt{slower}.
    \item A \href{https://github.com/maximecb/gym-minigrid}{gridworld} environment \citep{gym_minigrid}: the agent navigates in a randomly-generated gridworld composed of either empty cells, terminal lava cells, and goal cells where a reward of $1$ is collected at the first visit.
    \item A stochastic version of the gridworld environment with noisy rewards, where the noise is modelled as a Bernoulli distribution with a 15\% probability of error, i.e. receiving a reward of 1 in an empty cell or 0 in a goal cell.
\end{itemize}

@@

\bibliographystyle{splncs04}
\begin{thebibliography}{10}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }
\providecommand{\doi}[1]{https://doi.org/#1}

\bibitem{Bellman1957}
Bellman, R.: {Dynamic Programming}. Princeton University Press  (1957)

\bibitem{Bubeck2010}
Bubeck, S., Munos, R.: {Open Loop Optimistic Planning}. In: Proc. of COLT
  (2010)

\bibitem{Busoniu2013}
Buşoniu, L., Daniels, A., Munos, R., Babuska, R.: {Optimistic planning for
  continuous-action deterministic systems}. IEEE Symposium on Adaptive Dynamic
  Programming and Reinforcement Learning, ADPRL  (2013)

\bibitem{Busoniu2018}
Buşoniu, L., P{\'{a}}ll, E., Munos, R.: {Continuous-action planning for
  discounted infinite-horizon nonlinear optimal control with Lipschitz values}.
  Automatica  \textbf{92}(December),  100--108 (2018)

\bibitem{Cappe2013}
Capp{\'{e}}, O., Garivier, A., Maillard, O.A., Munos, R., Stoltz, G.:
  {Kullback-Leibler Upper Confidence Bounds for Optimal Sequential Allocation}.
  The Annals of Statistics  \textbf{41}(3),  1516--1541 (2013)

\bibitem{gym_minigrid}
Chevalier-Boisvert, M., Willems, L., Pal, S.: Minimalistic gridworld
  environment for openai gym. \url{https://github.com/maximecb/gym-minigrid}
  (2018)

\bibitem{Coquelin2007}
Coquelin, P.A., Munos, R.: {Bandit Algorithms for Tree Search}. Proc. of UAI
  (2007)

\bibitem{Coulom2006}
Coulom, R.: {Efficient Selectivity and Backup Operators in Monte-Carlo Tree
  Search}. In: {Proc. of International Conference on Computer and Games} (2006)

\bibitem{Grill2016}
Grill, J.B., Valko, M., Munos, R.: {Blazing the trails before beating the path:
  Sample-efficient Monte-Carlo planning}. In: Proc. of NeurIPS (2016)

\bibitem{Hren2008}
Hren, J.F., Munos, R.: {Optimistic planning of deterministic systems}. Lecture
  Notes in Computer Science  (2008)

\bibitem{Kearns2002}
Kearns, M., Mansour, Y., Ng, A.Y.: {A sparse sampling algorithm for
  near-optimal planning in large Markov decision processes}. In: Proc. of IJCAI
  (2002)

\bibitem{Kocsis2006}
Kocsis, L., Szepesv\'{a}ri, C.: Bandit based monte-carlo planning. In: Proc. of
  ECML (2006)

\bibitem{Leurent2018}
Leurent, E., Blanco, Y., Efimov, D., Maillard, O.A.: {Approximate Robust
  Control of Uncertain Dynamical Systems}. NeurIPS Machine Learning for
  Intelligent Transportation Systems Workshop  (2018)

\bibitem{Munos2014}
Munos, R.: {From Bandits to Monte-Carlo Tree Search: The Optimistic Principle
  Applied to Optimization and Planning}. Foundations and
  Trends{\textregistered} in Machine Learning  (2014)

\bibitem{Szorenyi2014}
Szorenyi, B., Kedenburg, G., Munos, R.: {Optimistic planning in Markov decision
  processes using a generative model}. In: Proc. of NeurIPS (2014)

\end{thebibliography}

>>>>

\let\accentvec\vec            %add before \documentclass
\documentclass[runningheads, envcountsame, a4paper]{llncs}
\let\spvec\vec                %add before \usepackage{amsmath}
\let\vec\accentvec

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}
\usepackage[hyphens]{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[misc]{ifsym}

@@

%
\title{Practical Open-Loop Optimistic Planning}
\toctitle{Practical Open-Loop Optimistic Planning}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Edouard Leurent\inst{1,2}(\Letter)\and
Odalric-Ambrym Maillard\inst{1}}
\tocauthor{Edouard~Leurent and
Odalric-Ambrym~Maillard}
%
\authorrunning{E. Leurent and O-A. Maillard}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{SequeL team, INRIA Lille - Nord Europe, France\\
\email{$\{$edouard.leurent,odalric.maillard$\}$@inria.fr}\and
Renault Group, France
%\\
%\email{edouard.leurent@renault.com}
}
%
\maketitle              % typeset the header of the contribution
%

@@

\emph{Monte-Carlo Tree Search} (\texttt{MCTS}) algorithms were historically motivated by the application of computer Go, and made a first appearance in the CrazyStone software \citet{Coulom2006}. They were later reformulated in the setting of Multi-Armed Bandits by \citet{Kocsis2006} with their \emph{Upper Confidence bounds applied to Trees} (\texttt{UCT}) algorithm. Despite its popularity \citep{Silver2016,Silver2017,Silver2018}, \texttt{UCT} has been shown to suffer from several limitations: its sample complexity can be at least doubly-exponential for some problems (e.g. when a narrow optimal path is hidden in a suboptimal branch), which is much worse than uniform planning \citep{Coquelin2007}. The \texttt{Sparse Sampling} algorithm of \citet{Kearns2002} achieves better worst-case performance, but it is still non-polynomial and doesn't adapt to the structure of the MDP. In stark contrast, the \emph{Optimistic Planning for Deterministic systems} (\texttt{OPD}) algorithm considered by \citet{Hren2008} in the case of deterministic transitions and rewards exploits the structure of the cumulative discounted reward to achieve a problem-dependent polynomial bound on sample complexity. A similar line of work in a deterministic setting is that of \texttt{SOOP} and \texttt{OPC} by \cite{Busoniu2013,Busoniu2018} though they focus on continuous action spaces. \texttt{OPD} was later extended to stochastic systems with the \emph{Open-Loop Optimistic Planning} (\OLOP) algorithm introduced by \citet{Bubeck2010} in the open-loop setting: we only consider sequences of actions independently of the states that they lead to. This restriction in the space of policies causes a loss of optimality, but greatly simplifies the planning problem in the cases where the state space is large or infinite. More recent work such as \texttt{St0p} \citep{Szorenyi2014} and \texttt{TrailBlazer} \citep{Grill2016} focus on the probably approximately correct (PAC) framework: rather than simply recommending an action to maximise the expected rewards, they return an $\epsilon$-approximation of the value at the root that holds with high probability. This highly demanding framework puts a severe strain on these algorithms that were developed for theoretical analysis only and cannot be applied to real problems.

@@

The corresponding complexity gain compared to the original Algorithm \ref{algo:kl-olop} is: 
\begin{equation*}
    \frac{C(\texttt{Lazy KL-OLOP})}{C(\KLOLOP)} = \frac{n}{K^{L-1}}
\end{equation*}
which highlights that only a subtree corresponding to the sample budget $n$ is processed instead of the search whole tree $\Tau$.
\end{property}
\begin{proof}
At episode $m = 1, \cdots, M$, we compute and store in memory the reward upper-bounds and U-values of all nodes in the subtree $\Tau_m^+$. Moreover, the tree $\Tau_m^+$ is constructed iteratively by adding K nodes at most L times at each episode from 0 to $m$. Hence, $|\Tau_m^+| = O(mKL)$.
This yields directly $C(\texttt{Lazy KL-OLOP}) = \sum_{m=1}^M O(mKL) = O(M^2KL)$.
\qed
\end{proof}

@@

By convention, $\mathcal{I}_0 = \{\emptyset\}$. From the definition of $\kappa_2$, we have that for any $\kappa'>\kappa_2$, there exists a constant C such that for any $h \geq 1$,
%\begin{equation*}
    $|\mathcal{I}_h| \leq C {\kappa'}^h$
%\end{equation*}
Hence, we also have $|\mathcal{J}_h| \leq K|\mathcal{I}_{h-1}| = O({\kappa'}^h)$.

@@

\diff{In order to bound this quantity, we reduce the question to the application of a deviation inequality. For all $1\leq t\leq L$, we have on the event $\{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\}$ that $\hat{\mu}_{a^*_{1:t}}(m) \leq U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t}) < 1$. Therefore, for all $0 < \delta < 1 - \mu(a^*_{1:t})$, by definition of $U^{\mu}_{a^*_{1:t}}(m)$:}

\begin{equation*}
    \diff{d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)+\delta) > \frac{f(m)}{T_{a^*_{1:t}}(m)}}
\end{equation*}

\diff{As $d$ is continuous on $(0,1)\times[0, 1]$, we have by letting $\delta \rightarrow 0$ that:}

\begin{equation*}
    \diff{d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)}}
\end{equation*}

\diff{Since d is non-decreasing on $[\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})]$,}

\begin{equation*}
    \diff{d(\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})) \geq d(\hat{\mu}_{a^*_{1:t}}(m), U^{\mu}_{a^*_{1:t}}(m)) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)}}
\end{equation*}

\diff{We have thus shown the following inclusion:}

\begin{equation*}
    \diff{\{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\} \subseteq \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}}(m) \text{ and } d(\hat{\mu}_{a^*_{1:t}}(m), \mu(a^*_{1:t})) \geq \frac{f(m)}{T_{a^*_{1:t}}(m)} \right\}}
\end{equation*}

\diff{Decomposing according to the values of $T_{a^*_{1:t}}(m)$ yields:}

\begin{equation*}
    \diff{\{U^{\mu}_{a^*_{1:t}}(m) \leq \mu(a^*_{1:t})\} \subseteq \bigcup_{n=1}^m \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}, n} \text{ and } d(\hat{\mu}_{a^*_{1:t}, n}, \mu(a^*_{1:t})) \geq \frac{f(m)}{n} \right\}}
\end{equation*}

\diff{We now apply the deviation inequality provided in Lemma 2 of Appendix A in \citep{Cappe2013}: $\forall \epsilon > 1$, provided that $0 < \mu(a^*_{1:t}) < 1$,}

\begin{equation*}
\diff{\probability{\bigcup_{n=1}^m \left\{ \mu(a^*_{1:t}) > \hat{\mu}_{a^*_{1:t}, n} \text{ and } n \dber(\hat{\mu}_{a^*_{1:t}, n}, \mu(a^*_{1:t})) \geq \epsilon \right\}} \leq e\ceil{\epsilon \log m}e^{-\epsilon}\,.}
\end{equation*}

\diff{By choosing $\epsilon = f(m)$, it comes}
\begin{align*}
    \diff{\probability{\eqref{eq:cond-ukl}} \leq \sum_{t=1}^L e\ceil{f(m)\log m}e^{-f(m)} = O(L\delta_m)}
\end{align*}

@@

\begin{lemma}[Confidence interval length and number of plays]
\label{lemma:ci-length}
Let $1 \leq h \leq L$, $a\in \mathcal{J}_h$ and $0 \leq h' < h$. Then  \eqref{eq:cond-dkl} is not satisfied if the following propositions are true:
\begin{equation}
\label{eq:sampled-enough-h}
   \forall 0\leq t\leq h', T_{a_{1:t}}(m) \geq \diff{2f(m)}(h+1)^2\gamma^{2(t-h-1)}
\end{equation}
and
\begin{equation}
\label{eq:sampled-enough}
   T_{a}(m) \geq \diff{2f(m)}(h+1)^2\gamma^{2(h'-h-1)}
\end{equation}
\end{lemma}
\begin{proof}
We start by providing an explicit upper-bound for the length of the confidence interval $U^{\mu}_{a_{1:t}} - L^{\mu}_{a_{1:t}}$. \diff{By Pinsker's inequality:}

@@

\diff{Hence for all $C>0$, }
\begin{equation*}
    \diff{\dber(p, q) \leq C   \implies 2(q - p)^2 < C  \implies p - \sqrt{C/2} < q < p + \sqrt{C/2}}
\end{equation*}
\diff{And thus, for all $b\in A^*$, by definition of $U^{\mu}$ and $L^{\mu}$:}
\begin{align*}
    \diff{U^{\mu}_{b}(m) - L^{\mu}_{b}(m) \leq \frac{S_b(m)}{T_b(m)} + \sqrt{\frac{f(m)}{2T_b(m)}} -  \left(\frac{S_b(m)}{T_b(m)} - \sqrt{\frac{f(m)}{2T_b(m)}}\right) 
    = \sqrt{\frac{2f(m)}{T_b(m)}}}
\end{align*}

@@

They are evaluated on the following tasks, using a discount factor of $\gamma=0.8$:
\begin{itemize}
    \item A \href{https://github.com/eleurent/highway-env/}{highway driving} environment \citep{highway-env}: a vehicle is driving on a road randomly populated with other slower drivers, and must make their way as fast as possible while avoiding collisions by choosing on the the following actions: \texttt{change-lane-left}, \texttt{change-lane-right}, \texttt{no-op}, \texttt{faster}, \texttt{slower}.
    \item A \href{https://github.com/maximecb/gym-minigrid}{gridworld} environment \citep{gym_minigrid}: the agent navigates in a randomly-generated gridworld composed of either empty cells, terminal lava cells, and goal cells where a reward of $1$ is collected at the first visit.
    \item A stochastic version of the gridworld environment with noisy rewards, where the noise is modelled as a Bernoulli distribution with a 15\% probability of error, i.e. receiving a reward of 1 in an empty cell or 0 in a goal cell.
\end{itemize}

@@

\section*{Acknowledgments}
This work has been supported by CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020, the French Ministry of Higher Education and Research, INRIA, and the French Agence Nationale de la Recherche.

\bibliographystyle{splncs04}
\bibliography{references}
